Where Do Population III Stars Form? The Effects of Radiative Feedback and Self-Shielding on the Host Halo Mass Distribution

### 2019-05-28 paper.tex
Addressing edits from John's paper-JHW-28May.pdf

% Abstract of the paper
\begin{abstract}
The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe. To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined. One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, which can destroy \hh{}, a necessary ingredient for the cooling and creation of Pop III stars. \hh{} self-shielding can alleviate the effect the LW background has on the \hh{} within halos, and is a process which is often neglected throughout the literature. In this work, we perform a cosmological simulation with a comoving volume of 1 Mpc$^{3}$ to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \enzo{}. We investigate the distribution of host halo masses and its relationship to the LW background intensity. Compared to the literature, our halos form Pop III stars at much lower masses due to the inclusion of \hh{} self-shielding. We see no relationship between the LW intensity and host halo mass. Most halos form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation. Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common. 
\end{abstract}{}

@@

%The first generation of stars transformed a cold and dark universe
by illuminating and enriching up their neighborhoods with radiation
and heavy elements. The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments are necessary for further star production and chemical enrichment. Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today. These stars are, by definition, metal-free (Population III; Pop III) and are thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}. A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}. The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.

Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep[][and more]{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars. These stars still are metal-poor, having metallicities of 10$^{-6}$ - 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos. But in which halos do these first generations of stars form? Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization. Learning about their host halos can also guide future telescopic surveys to observe Pop III galaxies which may lead to their direct observational evidence. Previous studies have investigated the possibility of finding Pop III systems. For example, \citet{Trenti09} found that metal-free halos may still be able to form at $z \approx$ 6, which offer the best chance at observing such primordial systems. They find that, given a certain rate of Pop III supernova per year, large sky surveys, such as the Large Synoptic Survey Telescope (LSST), should be able to detect the very luminous supernova. \citet{Trenti09} determine that unless the metal-free systems are particularly efficient at forming Pop III stars (star formation efficiencies > 10$^{-2}$), the upcoming James Webb Space Telescope (JWST) will not be able to detect such systems.

Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars. \citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15. In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time. \citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars. They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars. This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.

@@

@@

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux:
\begin{equation} \label{mthresh}
	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{.47}
\end{equation}
We will compare our results with this relation in future sections. \citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

%====================================================================
\section{Methods}
%====================================================================
\subsection{Simulation setup}
%====================================================================
We run and analyze a cosmological simulation with the adaptive mesh refinement (AMR) code \enzo{} \citep{Enzo} and the toolkit \yt{} \citep{yt_full_paper}. \enzo{} uses an N-body adaptive particle-mesh solver \citep{Efstathiou85, Couchman91, BryanNorman1997} to follow the dark matter (DM) dynamics. We use the nine-species (\hi, \hii, \hei, \heii, \heiii, e$^{-}$, H$_{2}$, H$_{2}^{+}$, H$^{-}$) non-equilibrium chemistry model \citep{Abel97, Anninos97}. This simulation is similar to the RP simulation in \citet[hereafter W12]{Wise12_RP}, but with updated cosmological and Pop III parameters, and the inclusion of \hh{} shielding.

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2000 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
\citet{Planck13_Cosmo}: $\Omega_{M}$ = 0.3175, $\Omega_{\Lambda}$ = 
0.6825, $\Omega_{DM}$ = 0.2685, and h = 0.6711, with the variables 
having their usual definitions. The simulation is run until $z$ = 9.32, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.

A time-dependent LW optically thin radiation background is applied in the simulation. This was fit in W12 (see their Eq. 16) and is consistent with the values in \citet{Trenti09_SFR}. The background evolution of the specific intensity takes the following form:
\begin{equation} \label{LWbg}
	\log_{10}(J_{\rm LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
\end{equation}
where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.

We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the radiation field. Centered on each metal-enriched and Pop III star, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile. These LW sources are added on top of the background intensity described above.
%====================================================================
\subsection{Star formation}
%====================================================================
In this section, we will discuss how we implement Pop III and metal-enriched star formation. We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars. For further details, we refer the reader to W12.

%====================================================================
\subsubsection{Pop III Star Formation and Feedback }
%====================================================================
The utilized Pop III star formation model is the same as in \citet{Wise08_Gal}. Each star particle represents a single massive star, and is formed in a cell when the following criteria are met: 
\begin{enumerate}
	\item a metallicity Z $\leq$ 5 $\times$ 10$^{-6}$ Z$_{\odot}$

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from W12 \citep{Hirano17}. This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after. Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. We are only tracking massive Pop III star formation.

@@

The lifetime of these particles is 20 Myr, during which they radiate 6000 hydrogen ionising photons per stellar baryon, or 1.13 $\times$ 10$^{46}$ photons s$^{-1}$ M$_{\odot}^{-1}$, which is appropriate for a Salpeter IMF. Their spectra are approximated with a monochromatic spectrum with an energy of 21.6 eV at a constant luminosity. After living for 4 Myr, the stars begin to return supernova energies of 6.8 $\times$ 10$^{48}$ erg s$^{-1}$ M$_{\odot}^{-1}$ back to their surroundings.

%====================================================================
\subsection{\hh{} Self-Shielding}
%====================================================================
We use the Sobolev-like approximation from \citet{Wolcott11} to model \hh{} self-shielding. To determine the \hh{} shielding factor, the column density of \hh{} needs to be calculated:
\begin{equation} \label{Nh2}
	N_{\rm H2} = n_{\rm H2}L_{\rm char} \ ,
\end{equation}
where n$_{\rm H2}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{\rm H2}$ is assumed to be constant. The method employed in this simulation is to define the characteristic length as:
\begin{equation} \label{Lchar}
	L_{\rm char} = \frac{\rho}{|\nabla \rho|}
\end{equation}
This Sobolev-like method determines the length over which gas with density $\rho$ is diminished. They found that the most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all Cartesian directions.

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determine that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, x $\equiv$ N$_{H_{2}}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ to the core as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor. The total number of \hh{} molecules within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum. The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background. Smaller mass halos can then form Pop III stars since \hh{} will stick around in the halo for a longer amount of time. We also see that for column densities at just under $10^{17} cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} at relatively low column densities.

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. By the end of the simulation, over 10\% of the box is ionized over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.

@@

As mentioned previously, Pop III stars form in our simulation only between 27.23 $\geq z \geq$ 9.39. During this time frame, a total of 688 Pop III stars form. The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}. Pop III star formation peaks at a redshift of 20 and slowly decreases. The star formation rate density does not fall to zero at the end of the simulation, since Pop III stars were still being produced when the simulation was cut off. The SFRD plotted here is particular for our box. Due to the small size of our box, we are unable to capture all of the cosmic variance. Therefore the SFRD is likely to change depending on the size and initial conditions of the box.

@@

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses < $1 M_{\odot}$. The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation. The histogram of the number of Pop III stars for all masses is projected on the right hand side. We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo. Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo. Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars. It should be noted that these halos aren't necessarily forming all of the Pop III stars at once. For example, a halo can form stars again if it din't host a supernova. The number of Pop III stars that form within a halo is indicative of the star formation history of that halo. Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side. Lines of constant star formation efficiency are overplotted. We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$. The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$.

>>>>

% Abstract of the paper
\begin{abstract}
The formation of Population III (Pop III) stars is a critical step in the evolution of the early universe. To understand how these stars affected their metal-enriched descendants, the details of how, why and where Pop III formation takes place needs to be determined. One of the processes that is assumed to greatly affect the formation of Pop III stars is the presence of a Lyman-Werner (LW) radiation background, that destroys \hh{}, a necessary coolant in the creation of Pop III stars. Self-shielding can alleviate the effect the LW background has on the \hh{} within halos. In this work, we perform a cosmological simulation to study the birthplaces of Pop III stars, using the adaptive mesh refinement code \textsc{Enzo}. We investigate the distribution of host halo masses and its relationship to the LW background intensity. Compared to previous work, halos form Pop III stars at much lower masses, up to a factor of a few, due to the inclusion of \hh{} self-shielding. We see no relationship between the LW intensity and host halo mass. Most halos form multiple Pop III stars, with a median number of four, up to a maximum of 16, at the instance of Pop III formation. Our results suggest that Pop III star formation may be less affected by LW radiation feedback than previously thought and that Pop III multiple systems are common. 
\end{abstract}{}

@@

The first generation of stars transformed a cold and dark universe
by illuminating and enriching up their neighborhoods with radiation
and heavy elements. The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments are necessary for further star production and chemical enrichment. Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today. These stars are, by definition, metal-free (Population III; Pop III) and are thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}. A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}. The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.

Once a halo becomes chemically enriched by the death of its Pop III stars, then by definition, it can no longer form more Pop III stars. This marks the end of metal-free star formation in that pregalactic object. Understanding the mixing of metals into the environment of these halos is necessary to constrain the reach of these metals and the effects they have for future star formation. Numerical studies have shown that turbulence within halos can mix metals well down to their resolution limit \citep{Wise08_Gal, Greif10, Smith15}. Stars will continue to form in halos, but with an increased metal abundance, these stars are now labeled as metal-enriched stars. These stars still are metal-poor, having metallicities of 10$^{-6}$ to 10$^{-2}$ of the solar abundance \citep{Chiaki16, Chiaki18, Ritter16}, have a direct chemical connection to Pop III stars, and survive until the present day \citep{Gnedin06, Tumlinson10, Griffen18, Magg18}. Understanding the formation and chemical abundance of second generation stars can provide more evidence and insight for the earlier generation of Pop III stars.

@@

Given the paradigm of hierarchical structure formation, halos grow through smooth accretion and successive mergers of smaller halos. But in which halos do these first generations of stars form? Their formation rates and locations are important to constrain because they influence the very beginnings of galaxy formation and cosmic reionization. Various semi-analytic investigations have been conducted to learn more about the halo collapse criterion, and thus, which halos can host Pop III stars. \citet{Tegmark97} discovered that halos can have a strongly redshift dependent, minimum baryonic mass of 10$^{6}$ M$_{\odot}$ at $z \approx$ 15. In particular, they derive an analytic expression for the fraction of \hh{} needed in a halo for efficient cooling, and determine which  halos can cool in a Hubble time. \citet{Visbal18} devised a semi-analytic model for the formation of Pop III stars and the transition to metal-enriched stars. They find that varying the Pop III star formation efficiency, the time from a Pop III supernova to metal-enriched star formation, the external enrichment of the halo, and the ionizing escape fraction, leads to large differences in the star formation history of Pop III and metal-enriched stars. This method is useful for exploring the wide parameter space of star formation in the early universe, and could lead to further constraints in the future.

@@

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They fit a simple analytic expression for the mass threshold of halos given a particular LW flux:
\begin{equation} \label{mthresh}
	M_{\rm TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{\rm LW}}{10^{-21}} \right)^{0.47} .
\end{equation}
We will compare our results with this relation in future sections. \citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01 J$_{\rm 21}$, although with sufficient \hh{} shielding, halos are able to cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background intensity of 1 J$_{21}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. \citet{OShea08} also find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

%====================================================================
\section{Methods}
%====================================================================
\subsection{Simulation setup}
%====================================================================
We run and analyze a cosmological simulation with the adaptive mesh refinement (AMR) code \textsc{Enzo} \citep{Enzo} and the toolkit \yt{} \citep{yt_full_paper}. \textsc{Enzo} uses an N-body adaptive particle-mesh solver \citep{Efstathiou85, Couchman91} to follow the dark matter (DM) dynamics. We use the nine-species (\hi, \hii, \hei, \heii, \heiii, e$^{-}$, H$_{2}$, H$_{2}^{+}$, H$^{-}$) non-equilibrium chemistry model \citep{Abel97, Anninos97}. This simulation is similar to the RP simulation in \citet[hereafter W12]{Wise12_RP}, but with updated cosmological and Pop III parameters, and the inclusion of \hh{} shielding.

We simulate a 1 Mpc$^{3}$ comoving box with a 256$^{3}$ base grid 
resolution and a dark matter paticle mass of 2000.54 M$_{\odot}$. It has a maximum refinement level of 12 which provides a maximal comoving resolution of $\sim$1 pc. The simulation is 
initialized with \music{} \citep{Hahn11_MUSIC} at $z$ = 130 and uses the cosmological parameters from the Planck collaboration best fit 
\citet{Planck13_Cosmo}: $\Omega_{\rm M}$ = 0.3175, $\Omega_{\Lambda}$ = 
0.6825, $\Omega_{\rm DM}$ = 0.2685, and h = 0.6711, with the variables 
having their usual definitions. The simulation is run until $z$ = 9.32, when it becomes too computationally expensive to continue. At this point, about 20\% of the volume is over 10\% ionized. We output 918 datasets,  roughly 0.5 Myr apart. In this paper, we focus only on outputs where Pop III stars have just formed, from $z$ = 27.23 to 9.39.

A time-dependent LW optically thin radiation background is applied in the simulation. This was fit in W12 (see their Eq. 16) and is consistent with the values in \citet{Trenti09_SFR}. The background evolution of the specific intensity takes the following form:
\begin{equation} \label{LWbg}
	\log_{10}(J_{\rm LW}/J_{21}) = A + Bz - Cz^{2} + Dz^{3} - Ez^{4}
\end{equation}
where $(A, B, C, D, E)$ = $(-2.567, 0.4562, - 0.02680, 5.882 \times 10^{-4}, - 5.056 \times 10^{-6})$ and J$_{21}$ is a specific intensity of 10$^{-21}$ erg s$^{-1}$ cm$^{-2}$ Hz$^{-1}$ sr$^{-1}$.  This form gives a maximum of $J_{\rm LW}/J_{21} = 0.85$ at a redshift of 13.5 and quickly and continually declines for higher redshifts. We use adaptive ray tracing \citep{Abel02_RT, Wise11_Moray} to evolve the ionizing radiation field. Centered on each metal-enriched and Pop III star particle, we model the \hh{} dissociating radiation field with an optically thin, inverse square profile. These LW sources are added on top of the background intensity described above.
%====================================================================
\subsection{Star formation}
%====================================================================
In this section, we briefly discuss our implementation of Pop III and metal-enriched star formation. We do not consider the formation and feedback from stellar remnants or asymptotic giant branch (AGB) stars. For further details, we refer the reader to W12.

%====================================================================
\subsubsection{Pop III Star Formation and Feedback }
%====================================================================
The utilized Pop III star formation model is the same as in \citet{Wise08_Gal} but with updated parameters. Each star particle represents a single massive star, and is formed in a cell when the following criteria are met: 
\begin{enumerate}
	\item a metallicity Z $\leq$ 5 $\times$ 10$^{-6}$ Z$_{\odot}$

@@

If within 1 pc, multiple cells meet this criteria, then a single Pop III star forms at the center of mass of these cells. The mass of the Pop III star is randomly sampled from an initial mass function (IMF) of the form:
\begin{equation} \label{IMF}
	f(\log M)dM = M^{-1.3} \exp \left[-\left( \frac{M_{\rm char}}{M}\right)^{1.6} \right]dM
\end{equation}
where M$_{\rm char}$ = 20 M$_{\odot}$ \citep{Hirano17}. This characteristic mass is different from the W12 choice of 100 M$_{\odot}$. This results in an exponential cutoff before M$_{\rm char}$ and a power-law IMF after. Once the cell meets the above criteria and the stellar mass is chosen, an equal amount of gas is removed from the grid in a sphere which contains twice the stellar mass that is centered on the new star particle. The new Pop III star then gains the mass-weighted velocity of the gas contained within that sphere. In this simulation, we do not track any small scale fragmentation which may form low mass stars \citep{Greif11_P3Cluster}. We are only tracking massive Pop III star formation.

@@

The lifetime of these particles is 20 Myr, during which they radiate 6000 hydrogen ionising photons per stellar baryon, or 1.13 $\times$ 10$^{46}$ photons s$^{-1}$ M$_{\odot}^{-1}$, which is appropriate for a Salpeter IMF \citep{Schaerer03}. Their spectra are approximated with a monochromatic spectrum with an energy of 21.6 eV at a constant luminosity. After living for 4 Myr, the stars begin to return supernova energies of 6.8 $\times$ 10$^{48}$ erg s$^{-1}$ M$_{\odot}^{-1}$ back to their surroundings.

%====================================================================
\subsection{\hh{} Self-Shielding}
%====================================================================
We use the Sobolev-like approximation from \citet{Wolcott11} to model \hh{} self-shielding. To determine the \hh{} shielding factor, the column density of \hh{} needs to be calculated:
\begin{equation} \label{Nh2}
	N_{\rm H2} = n_{\rm H2}L_{\rm char} \ ,
\end{equation}
where n$_{\rm H2}$ is the number density of \hh{} and L$_{\rm char}$ is a characteristic length over which n$_{\rm H2}$ is assumed to be constant. The method employed in this simulation is to define the characteristic length as:
\begin{equation} \label{Lchar}
	L_{\rm char} = \frac{\rho}{|\nabla \rho|} \ . 
\end{equation}
This Sobolev-like method determines the length over which gas with density $\rho$ is diminished. They found that the most accurate, non-ray tracing, method is to use a single Sobolev-like length determined from the mean Sobolev-like length over all Cartesian directions.

Upon numerically calculating the shielding factor of \hh{} for simulated protogalaxies, Wolcott-Green et al. determined that a slight adjustment to the shielding factor from \citet{Draine96} is sufficient to account for inaccuracies at higher temperatures. The implemented shielding factor is then (see Eq. 10 in \citet{Wolcott11}):
\begin{equation} \label{shield}
	\begin{multlined}
	f_{\rm sh}(N_{\rm H2}, T) = \frac{0.965}{(1+x/b_{5})^{1.1}} + \frac{0.035}{(1+x)^{0.5}}  \times \\ \exp [-8.5 \times 10^{-4} (1+x)^{0.5}]
	\end{multlined}
\end{equation}
Here, x $\equiv$ N$_{\rm H2}$/5 $\times$ 10$^{14}$ cm$^{-2}$, b$_{5}$ $\equiv$ b/10$^{5}$ cm s$^{-1}$, and $b$ is the Doppler broadening parameter. This shielding factor acts as a multiplier to the \hh{} dissociation rate, where if the shielding factor equals one, there is no shielding, and zero if there is maximum shielding.

%====================================================================
\subsection{Analytic Calculation of the Shielding Factor for a Static Halo}
%====================================================================
To demonstrate how the shielding factor changes as a function of halo mass and redshift, we can examine $N_{\rm H2}$ between the core and halo virial radius as a function of halo mass for an isothermal halo, with a constant \hh{} fraction, and use Equation \ref{shield} to calculate the shielding factor. The \hh{} molecule number density within the halo is given by 
\begin{equation} \label{numberh2}
	n_{\rm H2}(r) = f_{\rm H2} \frac{\rho_{0}R^{2}_{\rm vir}}{\mu m_{\rm H} r^{2}}
\end{equation}
where $\mu = 1.22$ is the mean molecular weight, $\rho_{0} = 200 \rho_{c} / 3$ is the density at the virial radius, and $\rho_{c} = 3 \rm{H}_{0}^{2} / 8 \pi \rm{G} (1+z)^3$ is the critical density. The column density is then equation \ref{numberh2} integrated from the radius of the core to the virial radius, where the core has a radius of $f_{c} R_{\rm vir}$: 
\begin{equation} \label{columnh2}
	N_{\rm H2} = f_{\rm H2} R_{\rm vir} \frac{200 \rho_{c}}{3 \mu m_{\rm H}} \left(\frac{1}{f_{c}} - 1 \right)
\end{equation}

For $\rm{H}_{0} = 70 \ \rm{km} \ \rm{s}^{-1} \ \rm{Mpc}^{-1}$, a typical \hh{} fraction of $f_{\rm H2} = 10^{-4}$, and assuming the Doppler broadening parameter, $b$, is equal to the circular velocity of the halo, Equation \ref{columnh2} and Equation \ref{shield} will give the shielding factor for a given core radius, $f_{c}$, and redshift. Figure \ref{fig:shield_mass} shows the shielding factor as a function of halo mass, for redshifts $z = 9$, $15$, and $25$ in red, blue and black, respectively. The solid lines indicate a core radius of $f_{c} = 10^{-2}$ and the dashed lines a core radius of $f_{c} = 10^{-4}$. Across the top axis and plotted as a green line, the shielding factor as a function of \hh{} column density is shown for a circular velocity of 10 km/s. At each redshift, all halo masses, and for each core radius, we see the shielding factor is significantly smaller than one, implying that \hh{} shielding for these halos is almost at a maximum. The shielding factor will then significantly decrease the dissociation rate of \hh{}, allowing for the presence of \hh{} within a LW background. Smaller mass halos can then form Pop III stars since \hh{} will survive in the halo for a longer amount of time. We also see that for column densities at just under $10^{17} \rm cm^{-2}$, the shielding factor quickly drops to 0.1 for a halo with this particular circular velocity, showing that \hh{} shielding can affect the dissociation rate of \hh{} at relatively low column densities.

@@

To ensure that our box is representative of a typical piece of the universe, Figure \ref{fig:hmf} shows the simulated halo mass function along with the analytic Sheth-Tormen mass function at $z$ = 9.3. The analytic function closely matches our simulation until the mass resolution of our simulation is unable to resolve below 10$^{5}$ M$_{\odot}$ halos that contain $\approx$ 50 particles. After a sufficient amount of time after the beginning of the simulation, enough matter has collapsed to begin forming Pop III stars throughout the box. These stars either become black holes or supernova at the end of their lives, with the latter resulting in an expulsion of metals into the star's surroundings. Metal-enriched star formation begins to take place as soon as enough metals are present within a halo. In the meantime, halos form and merge with one another, resulting in a wide variety of galaxies, and reionization starts to take place. By the end of the simulation, 20\% of the box is ionized over 10\%, as can be seen in Figure \ref{fig:JLW_xe_mass}, which also shows the mass weighted LW intensity as a function of time, and temperature projections of the box at certain points in time.

@@

In our simulation, 688 Pop III stars form between 27.23 $\geq z \geq$ 9.39. The corresponding star formation rate density can be seen in Figure \ref{fig:pop3_SFR_bar}. Pop III star formation peaks at $1.9 \times 10^{-4}$ at $z = 21.3$ and slowly decreases. The star formation rate density does not fall to zero at the end of the simulation, since Pop III stars were still being produced when the simulation was cut off. The SFRD plotted here is particular for our box. Due to the small size of our box, we are unable to capture all of the cosmic variance. Therefore the SFRD is likely to change depending on the size and initial conditions of the box.

@@

%====================================================================
\subsection{Lyman-Werner background for Pop III host halos}
%====================================================================

@@

We now inspect the number of Pop III stars and the total mass of Pop III stars per halo. Again, we are only tracking massive stars, not any stars that may form out of fragmented gas with masses < $1 M_{\odot}$. The left panel of Figure \ref{fig:num_p3} shows the number of Pop III stars per halo for a given halo mass, just after star formation. The histogram of the number of Pop III stars for all masses is projected on the right hand side. We find that a median number of four Pop III stars form per halo, with a maximum of 16 Pop III stars forming per halo. Since we did not restrict the number of Pop III stars that can form in a halo, we find that the conditions are often sufficient for multiple Pop III stars to form in a single halo. Out of the halos forming Pop III stars, only 16\% of them form single Pop III stars, whereas 54\% form between two and five Pop III stars. It should be noted that these halos are not necessarily forming all of the Pop III stars at once. For example, a halo can form stars again if it did not host a supernova. The number of Pop III stars that form within a halo is indicative of the star formation history of that halo. Figure \ref{fig:totp3mass_halomass_sidehist} shows the total mass of Pop III stars per halo for a given halo mass, where the histogram of the total Pop III mass for all halos is projected on the right hand side. Lines of constant star formation efficiency are overplotted. We find that most of our Pop III stars are forming between 10$^{-4}$ < f$_\star$ < 10$^{-3}$. The mean total mass of Pop III stars for all halos is 195 M$_{\odot}$. Note that the mass of the Pop III stars depends on the chosen IMF.
